\vspace{-0.25em}\thetitle

### 2009-07-31 paper.tex
...

\newfootnote{\ksidealnote}{If the K-S test were perfect, the pragmatic baseline would be uniform. The fact that it is not demonstrates the imperfection of the K-S test.}

@@

Part of the reason the model of flow generation as mixtures of a basic set of behaviors is not obvious and has not previously been noted is likely that with convex linear combinations, so many different combinations can be created.
Moreover, the analytical tools to extract this structure have only existed for a few years.
In our model recovery procedure, we use a subspace segmentation algorithm published in 2007~\cite{Ma07}, two \caps{NMF} algorithms published in 2001 and 2008, respectively~\cite{Lee01,Kim08:anls}, and a low-rank \caps{NMF} initialization technique published for the first time here.
And these techniques are still quite immature:
they will only improve over time, yielding even better recovery of the model parameters.
Such improvements will immediately improve the performance of the prediction methods employed in this paper.

@@

% TODO: mention the two dimension structure assumption.
% TODO: mention the five packets in the results somewhere.

>>>>

\newfootnote{\ksidealnote}{If the K-S test were perfect, the pragmatic ideal baseline would be uniform. The fact that it is not demonstrates the imperfection of the K-S test.}

@@

Given that the statistical model we have proposed for flow behavior is fairly simple---and finite mixture modeling is a well established field that has been studied since 1894~\cite{McLachlan00}.
Traditional approaches, however, have only applied to parametric probability distributions.
The distributions found in network traffic, however, are very distinctly non-parametric.
They are lumpy, unruly and generally quite ugly.
This is due largely to the fact that behaviors found in computer networks are not the by-products of smooth, natural phenomena, but rather of man-made artificial systems, following arbitrary, complex and capricious rules.

The numerical techniques needed to tackle non-parametric mixture modeling have only very recently become available.
In our model recovery procedure, we use a subspace segmentation algorithm published in 2007~\cite{Ma07}, two \caps{NMF} algorithms published in 2001 and 2008, respectively~\cite{Lee01,Kim08:anls}, and a low-rank \caps{NMF} initialization technique published for the first time here.
All of these techniques are still quite immature:
New \caps{NMF} algorithms have been regularly proposed since Lee and Seung's seminal paper in 2001.
Their algorithms are still the most well-known, and often the most reliable despite their various shortcomings~\cite{Langville06}.
they will only improve over time, yielding even better recovery of the model parameters.
Such improvements will immediately improve the performance of the prediction methods employed in this paper.

% Part of the reason the model of flow generation as mixtures of a basic set of behaviors is not obvious and has not previously been noted is likely that with convex linear combinations, so many different combinations can be created.
% Moreover, the analytical tools to extract this structure have only existed for a few years.
% In our model recovery procedure, we use a subspace segmentation algorithm published in 2007~\cite{Ma07}, two \caps{NMF} algorithms published in 2001 and 2008, respectively~\cite{Lee01,Kim08:anls}, and a low-rank \caps{NMF} initialization technique published for the first time here.
% And these techniques are still quite immature:
% they will only improve over time, yielding even better recovery of the model parameters.
% Such improvements will immediately improve the performance of the prediction methods employed in this paper.

@@

% TODO: mention the two dimension structure assumption.

\vfill
\pagebreak
